PhD Proposal

### 2022-04-22 abstract/abstract.tex
continuo abstract

proposed its use together with the so-called FM-index \cite{fmindex}.\\

@@

management of the multiallelic case \cite{mpbwt}. \\

@@

The \textbf{Burrows-Wheeler Transform (\textit{BWT})} \cite{bwt} was introduced

@@

\cite{sdsl}, one of the most important C++ library used in bioinformatics. As

@@

al. \cite{rindex}, was called \textbf{r-index} and corresponds to the

@@

the text) cd\cite{lce} and \textbf{straight-line programs (\textit{SLP})}
\cite{slp} (for \textit{random access} and \textit{lce queries} over the

@@

developed in \textit{BIAS}.

>>>>

proposed its use together with the so-called FM-index
%\cite{fmindex}
.\\

@@

management of the multiallelic case
% \cite{mpbwt}
. \\

@@

The \textbf{Burrows-Wheeler Transform (\textit{BWT})}
% \cite{bwt}
was introduced

@@

% \cite{sdsl}
, one of the most important C++ library used in bioinformatics. As

@@

al.
% \cite{rindex}
, was called \textbf{r-index} and corresponds to the

@@

the text)
% \cite{lce}
and \textbf{straight-line programs (\textit{SLP})}
% \cite{slp}
(for \textit{random access} and \textit{lce queries} over the

@@

developed in \textit{BIAS}.\\
\textbf{AGGIUNGERE ALMENO DUE O TRE TOPIC DI RICERCA}.\\
From a more technical point of view, during both my bachelor degree and master
degree, mainly focused on the use of the \textbf{C++ programming language},
mainly due to the availability of efficient libraries that have now become
standard in the bioinformatics field, as the already cited \textit{SDSL}. In
addition to \textit{C++}, however, I had the opportunity to deepen
\textbf{Python}, with libraries such as \textit{biopython} and \textbf{Rust},
with recently developed libraries such as \textit{bio-rust} (and therefore not
yet complete from an algorithmic point of view). \\
A lack of knowledge that I intend to fill during the PhD is the use of efficient
algorithms based on parallel computing on GPU, algorithms that are increasingly
in use in both bioinformatics and systems biology. \\
To conclude this proposal I also point out the intention to maintain contacts
with various researchers, initially obtained during the work on the project of
the master’s thesis, including Christina Boucher (University of Florida), Travis
Gagie (Dalhousie University) etc$\ldots$ in order to make my PhD program more
complete. 
